Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

## Models 
```{r Linear Regression}
# Create the recipe for all models
rec <- origin %>% 
    recipe(value ~ lat + lon + state)

@@

>>>>

## Models 
```{r Linear Regression}
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ lat + lon + state)

@@

## Results
Describe the development of your 3 prediction models (or 4 models, if working in a group) and
how you compared their performance. 
Be sure to describe the splitting of training and testing datasets 
and the use of cross-validation to evaluate prediction metrics. 
Remember that the primary metric for your prediction model will be root-mean-squared error (RMSE). 
Your results should include 
at least one visualization demonstrating the prediction performance of your models. 
You should also include 
a table summarizing the prediction metrics (including RMSE) across all of the models that you tried.

1. Based on test set performance, at what locations does your model give predictions that
are closest and furthest from the observed values? What do you hypothesize are the
reasons for the good or bad performance at these locations?
2. What variables might predict where your model performs well or not? For example, are
their regions of the country where the model does better or worse? Are there variables
that are not included in this dataset that you think might improve the model performance
if they were included in your model?
3. There is interest in developing more cost-effect approaches to monitoring air pollution
on the ground. Two candidates for replacing the use of ground-based monitors are
numerical models like CMAQ and satellite-based observations such as AOD. How well do
CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction
performance of your model change when CMAQ or aod are included (or not included) in
the model?
4. The dataset here did not include data from Alaska or Hawaii. Do you think your model
will perform well or not in those two states? Explain your reasoning

## Discussion
Putting it all together, what did you learn from your data and your model performance?
• Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.
• Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?
• Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?
• Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).
